---
title: "Lab 10"
author: "Alessandra Puig-Santana"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(usethis)
library(janitor)

# New packages 

library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)

```


## beepr beeps 
Use the function `beep()` in the beepr package to make an audio alert when your code is done running 
```{r, eval = FALSE}
# eval = FALSE, so that it doesn't run every time
# Adding a number to beep() will have different sounds.
# For each value in this vector called "i"

for (i in rev(seq(1:9999))) {
  
  print(paste(i, "bottles of beer on the wall"))
  
}

# beep(5)
```

## praise and cowsay 

Packages built with a single purpose: to be kind and fun

```{r}
praise("${creating}, Batman - this code is...${ADJECTIVE}!!!")
```

Use cowsay::say() to make a character say something to you

Use usethis::use_git() on the Console to make sure you create a git tab on your project

Use usethis::use_github() to create a repository on Github
- then takes you to the repository
- there update the branch name
- one changed, copy and paste the code that it provides and then paste it on to the terminal

## Paletteer to access thousands of color palettes 
```{r}
storms %>%
  group_by(name) %>%
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>%
  slice_min(n = 10, min_pressure) %>%
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("palettetown::squirtle")
```


## One spatial data example
- read_sf allows you to read in spacial data
```{r}
vegetation <- read_sf("doc.kml") %>%
  select(Name) %>%
  clean_names

ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) +
  theme_minimal() +
  scale_fill_paletteer_d("ggthemes::manyeys") +
  labs(title = "Jornada Basin LTER Vegetation",
       caption = "Source: Jornada LTER")

# Update theme to theme_mininal
# Fill color change based on the vegetation
# Color of line to NA (color = NA)
```


```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5)
```

